\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}

\title{Adaptive Partitioning under Dynamic Skew in Stream Processing Workloads}
\author{Anonymous}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We study Kafka-style stream ingestion when key popularity shifts over time: a moving hot key changes which partition becomes overloaded. A default hash partitioner binds each key to a single partition, which is ideal for per-key ordering but can trap evolving skew on one broker. We describe a lightweight producer-side partitioner that balances short-term stickiness with load steering, and we outline an experimental methodology using a synthetic workload generator with configurable phase and skew intensity.
\end{abstract}

\section{Introduction}
Log-structured publish--subscribe systems partition topics for parallelism and fault tolerance. Hash partitioning colocates all events for a key, preserving consumer semantics at the cost of sensitivity to skew. Real workloads exhibit \emph{dynamic} skew: advertising budgets, trending entities, or regional spikes move the hot key set. We motivate producer-side adaptation that reacts to observed imbalance without requiring cluster topology changes.

\section{Design}
Let partitions be $\{0,\ldots,P-1\}$. A classical partitioner chooses $h(k) \bmod P$ for key $k$. Our adaptive variant maintains a short TTL \emph{sticky} assignment per key to avoid thrashing ordering, but if the preferred partition's recent count exceeds a slack factor times the mean load, the producer steers the key to the least-loaded partition and refreshes the sticky route.

\section{Methodology}
We evaluate with a synthetic generator that (i) sends a configurable fraction of traffic to a moving hot key every $\tau$ milliseconds, and (ii) sweeps hot-key fraction for fixed $\tau$. Consumer lag and end-to-end throughput are logged to \texttt{results/} and plotted via \texttt{plots/generate\_plots.py}.

\section{Results}
Populate \texttt{results/lag.txt} and \texttt{results/throughput.txt} with measured trials; figures go in \texttt{plots/}.

\section{Conclusion}
Producer-side adaptive routing is a low-intrusion knob for evolving skew; trade-offs versus strict per-key ordering deserve quantification per application.

\end{document}
